Gammapy: A Python package for gamma-ray astronomy

### 2022-08-08 src/ms-review.tex
Apply suggestions from code review
Co-authored-by: Quentin Remy <quentin.remy@live.fr>

Figure~\ref{fig:data_flow} shows an overview of the different sub-packages and
their relation to each other. The \code{gammapy.data} and \code{gammapy.irf}
sub-packages define data objects to represent DL3 data, such as
event lists and IRFs as well as functionality
to the DL3 data from disk into memory. The \code{gammapy.makers} sub-package
contains the functionality to reduce the DL3 data to binned maps.
Binned maps and datasets, which represent a collection of binned
maps are defined in the \code{gammapy.maps} and \code{gammapy.datasets}
sub-packages respectively. Parametric models, which are defined in
\code{gammapy.modeling}, are used to jointly model a combination
of datasets for example to create source catalogs. Estimator classes,
which are contained in \code{gammapy.estinators} are used to
compute higher level science products such as flux and signficance maps,
light curves or flux points. Finally there is a \code{gammapy.analysis}
sub-package which provides a high level interface for executing analyses
defined from configuration files. In the following sections we will
introduce all sub-packages and their functionality in more detail.

@@

\paragraph{Point spread function:}
\gammapy allows user to treat different kinds of PSFs,
in particular, parametric multi-dimensional Gaussians (\code{EnergyDependentMultiGaussPSF})
or King profile functions (\code{PSFKing})
one. The \code{EnergyDependentMultiGaussPSF} class is able to handle up to three
Gaussians, defined in terms of amplitudes and sigma given for each true energy
and offset angle bin. Similarly, \code{PSFKing takes} into account the gamma and
sigma parameters as defined here. The \code{ParametricPSF} allows to create a
PSF with a representation different from Gaussian(s) or King profile(s).
Finally, the user can take advantage from the \code{PSFMap} class, which creates
a multi-dimensional map of the PSF in WCS coordinates. At each position, a PSF
kernel map (\code{PSFKernel}) provides a PSF as a function of the true energy.
The creation of PSF kernel maps, where the PSF is defined for each
sky-position, is also given to the user. The latter two can speed up analyses.

@@

Following the factorisation The models objects are grouped
into the following categories:

@@

The models follow a naming scheme which contains the category as a suffix to
the class name.

The spectral models include a special class of normed models, which have a
dimension-less normalisation. These spectral models feature a norm parameter
instead of amplitude and are named using the NormSpectralModel suffix. They
must be used along with another spectral model, as a multiplicative correction
factor according to their spectral shape. They can be typically used for
adjusting template based models, or adding a EBL correction to some analytic
model. The analytic spatial models are all normalized such as they integrate to
unity over the sky but the template spatial models may not, so in that special
case they have to be combined with a \code{NormSpectralModel}.

@@

The \code{Fit} class provides methods to fit i.e., optimise parameters and estimate
parameter errors and correlations. It interfaces with a \code{Datasets} object, which
in turn is connected to a \code{Models} object containing the model parameters in its
\code{Parameters} object. Models can be unique for a given dataset, or contribute to
multiple datasets and thus provide links, allowing e.g., to do a joint fit to
multiple IACT datasets, or to a joint IACT and \fermi dataset. Many
examples are given in the tutorials.

@@

The Fit class provides a uniform interface to multiple fitting backends:
“minuit”~\citep{iminuit}, “scipy”,~\citep{2020SciPy-NMeth}, and
“sherpa”~\citep{sherpa-2005,sherpa-2011}. Note that, for now, covariance matrix
and errors are computed only for the fitting with MINUIT. However depending on
the problem other optimizers can better perform, so sometimes it can be useful
to run a pre-fit with alternative optimization methods. In future we plan to
extend the supported fitting backends, including for example MCMC solutions.
\footnote{a prototype is available in gammapy-recipes,
	\url{https://gammapy.github.io/gammapy-recipes/_build/html/notebooks/mcmc-sampling-emcee/mcmc_sampling.html}
}

@@

\begin{table*}[ht!]
    \begin{center}
        \begin{tabular}{llll}
         \hline
         Class Name & Shortcut & Description & Reference\\
         \hline
         \code{SourceCatalog3FGL} & \code{"3fgl"} & 3\textsuperscript{rd} catalog of \fermi sources & \cite{3FGL} \\
         \code{SourceCatalog4FGL} & \code{"4fgl"} & 4\textsuperscript{th} catalog of \fermi  sources & \cite{4FGL} \\
         \code{SourceCatalog2FHL} & \code{"2fhl"} & 2\textsuperscript{nd} catalog high-energy \fermi  sources & \cite{2FHL} \\
         \code{SourceCatalog3FHL} & \code{"3fhl"} & 3\textsuperscript{rd} catalog high-energy \fermi  sources & \cite{3FHL} \\
         \code{SourceCatalog2HWC} & \code{"2hwc"} & 2\textsuperscript{nd} catalog of \hawc sources & \cite{2HWC} \\
         \code{SourceCatalog3HWC} & \code{"3hwc"} & 3\textsuperscript{rd} catalog of \hawc sources & \cite{3HWC} \\
         \code{SourceCatalogHGPS} & \code{"hgps"} & \hess Galactic Plane Survey catalog & \cite{HGPS} \\
         \code{SourceCatalogGammaCat} & \code{"gammacat"} & Open source data collection & \citep{gamma-cat} \\
         \hline
         \end{tabular}
    \end{center}
    \label{tab:catalogs}
    \caption{Overview of supported catalogs in \code{gammapy.catalog}.}
\end{table*}

@@

%\subsection{gammapy.utils}
\label{ssec:gammapy-utils}
Utility functions...

>>>>

Figure~\ref{fig:data_flow} shows an overview of the different sub-packages and
their relation to each other. The \code{gammapy.data} and \code{gammapy.irf}
sub-packages define data objects to represent DL3 data, such as
event lists and IRFs as well as functionality
to the DL3 data from disk into memory. The \code{gammapy.makers} sub-package
contains the functionality to reduce the DL3 data to binned maps.
Binned maps and datasets, which represent a collection of binned
maps are defined in the \code{gammapy.maps} and \code{gammapy.datasets}
sub-packages respectively. Parametric models, which are defined in
\code{gammapy.modeling}, are used to jointly model a combination
of datasets for example to create source catalogs. Estimator classes,
which are contained in \code{gammapy.estimators} are used to
compute higher level science products such as flux and signficance maps,
light curves or flux points. Finally there is a \code{gammapy.analysis}
sub-package which provides a high level interface for executing analyses
defined from configuration files. In the following sections we will
introduce all sub-packages and their functionality in more detail.

@@

\paragraph{Point spread function:}
\gammapy allows user to treat different kinds of PSFs,
in particular, parametric multi-dimensional Gaussians (\code{EnergyDependentMultiGaussPSF})
or King profile functions (\code{PSFKing})
one. The \code{EnergyDependentMultiGaussPSF} class is able to handle up to three
Gaussians, defined in terms of amplitudes and sigma given for each true energy
and offset angle bin. Similarly, \code{PSFKing takes} into account the gamma and
sigma parameters as defined here. The \code{ParametricPSF} allows to create a
PSF with a representation different from Gaussian(s) or King profile(s).
Finally, the user can take advantage from the \code{PSFMap} class, which creates
a multi-dimensional map of the PSF in sky coordinates. At each position, a PSF
kernel map (\code{PSFKernel}) provides a PSF as a function of the true energy.
The creation of PSF kernel maps, where the PSF is defined for each
sky-position, is also given to the user. The latter two can speed up analyses.

@@

Following the factorisation the models objects are grouped
into the following categories:

@@

The models follow a naming scheme which contains the category as a suffix to
the class name.
The spectral models include a special class of normed models, named using the NormSpectralModel suffix.
normalisation. These spectral models feature a dimension-less norm parameter
instead of a physical amplitude parameter. They
must be used along with another spectral model, as a multiplicative correction
factor according to their spectral shape. They can be typically used for
adjusting template based models, or adding a EBL correction to some analytic
model. The analytic spatial models are all normalized such as they integrate to
unity over the sky but the template spatial models may not, so in that special
case they have to be combined with a \code{NormSpectralModel}.

@@

The \code{Fit} class provides methods to fit i.e., optimise parameters and estimate
parameter errors and correlations. It interfaces with a \code{Datasets} object, which
in turn is connected to a \code{Models} object containing the model parameters in its
\code{Parameters} object. Models can be unique for a given dataset, or contribute to
multiple datasets, allowing e.g., to do a joint fit to
multiple IACT datasets, or to a joint IACT and \fermi dataset. Many
examples are given in the tutorials.

@@

The Fit class provides a uniform interface to multiple fitting backends:
“minuit”~\citep{iminuit}, “scipy”,~\citep{2020SciPy-NMeth}, and
“sherpa”~\citep{sherpa-2005,sherpa-2011}. Note that, for now, covariance matrix
and errors are computed only for the fitting with MINUIT. However depending on
the problem other optimizers can better perform, so sometimes it can be useful
to run a pre-fit with alternative optimization methods. In future we plan to
extend the supported fitting backends, including for example solutions based on Markov chain Monte Carlo.
\footnote{a prototype is available in gammapy-recipes,
	\url{https://gammapy.github.io/gammapy-recipes/_build/html/notebooks/mcmc-sampling-emcee/mcmc_sampling.html}
}

@@

\begin{table*}[ht!]
    \begin{center}
        \begin{tabular}{llll}
         \hline
         Class Name & Shortcut & Description & Reference\\
         \hline
         \code{SourceCatalog3FGL} & \code{"3fgl"} & 3\textsuperscript{rd} catalog of \fermi sources & \cite{3FGL} \\
         \code{SourceCatalog4FGL} & \code{"4fgl"} & 4\textsuperscript{th} catalog of \fermi  sources & \cite{4FGL} \\
         \code{SourceCatalog2FHL} & \code{"2fhl"} & 2\textsuperscript{nd} catalog high-energy \fermi  sources & \cite{2FHL} \\
         \code{SourceCatalog3FHL} & \code{"3fhl"} & 3\textsuperscript{rd} catalog high-energy \fermi  sources & \cite{3FHL} \\
         \code{SourceCatalog2HWC} & \code{"2hwc"} & 2\textsuperscript{nd} catalog of \hawc sources & \cite{2HWC} \\
         \code{SourceCatalog3HWC} & \code{"3hwc"} & 3\textsuperscript{rd} catalog of \hawc sources & \cite{3HWC} \\
         \code{SourceCatalogHGPS} & \code{"hgps"} & \hess Galactic Plane Survey catalog & \cite{HGPS} \\
         \code{SourceCatalogGammaCat} & \code{"gammacat"} & Open source data collection & \cite{gamma-cat} \\
         \hline
         \end{tabular}
    \end{center}
    \label{tab:catalogs}
    \caption{Overview of supported catalogs in \code{gammapy.catalog}.}
\end{table*}

@@

%\subsection{gammapy.utils}
%\label{ssec:gammapy-utils}
%Utility functions...
